Full Title

### 2019-10-15 prisc-2020/acmart-sigplanproc/acmart-sigplanproc-template.tex
prisc 2020 draft

Iris is a higher-order concurrent separation logic framework. Its support of higher-order ghost state makes Iris a great candidate for complex reasoning about \textit{state}. This is exactly what we need for reasoning about a machine, where computation \textit{is} state manipulation.

@@

\subsection{Definition of the Logical Relation}
The logical relation is a unary relation that relates a word to  \textit{capability safety} (fig. \ref{fig:relation}). The definition is the Iris implementation of the logical relation defined by Skorstensgaard et. al. \cite{skorstensgaard}. The value relation $\mathcal{V}$ is an Iris relation of type $World \to Word \to iProp$ (we will later discuss what the World type is). We then define the register relation $\mathcal{R}$ as the validity of each word that the register state maps to.

@@

\subsection{The Iris Implementation of the Context}
In the expression relation, the \textsf{context} contains the ghost resources necessary to run a program pointed to by the program counter. When the program has finished running, ownership of these resources is given back. To start out, the running program gets full ownership of all machine registers. A ghost register will be represented by the full ownership of the map from RegName to Word. We write 
$$ r \mapsto_r w$$
to indicate that registers r currently contains the word w. The context will contain such a statement for each register in the register map.

@@

>>>>

Iris is a higher-order concurrent separation logic framework. Its support of higher-order ghost state makes Iris a great candidate for complex reasoning about \textit{state}. This is exactly what we need for reasoning about a machine, where computation \textit{is nothing but} state manipulation.

@@

\subsection{Definition of the Logical Relation}
The logical relation is a unary relation that relates a word to  \textit{capability safety}. Figure \ref{fig:relation}) describes the Iris implementation of the logical relation defined by Skorstensgaard et. al. \cite{skorstensgaard}. The value relation $\mathcal{V}$ is an Iris relation of type $World \to Word \to iProp$ (we will later discuss what the World is). We then define the register relation $\mathcal{R}$ as the validity of each word that the register state maps to.

@@

\subsection{The Context}
In the expression relation, the \textsf{context} contains the ghost resources necessary to run a program pointed to by the program counter. When the program has finished running, ownership of these resources is given back. To start out, the running program gets full ownership of all machine registers. A ghost register will be represented by the full ownership of the map from RegName to Word. We write 
$$ r \mapsto_r w$$
to indicate that registers r currently contains the word w. The context will contain such a statement for each register in the register map.

@@

\subsection{The World}
